The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-10 rational.tex
intro

At this point we have constructed a strange mixing of two functions;
`inputs' of one form `outputs' of the other. If {{(1/alpha1,alpha2)}}
is held by one subcomputation and {{1/alpha2,alpha1)}} is held by
another subcomputation, these `remixed functions' form a communication
channel between the subcomputations -- unifying {{1/alpha1}} with
{{R}} in one subcomputation fixes it in the other. Depending on the
choice of the type {{a}}, an arbitrary number of bits may be
communicated. The dual reading of the above, with additive functions
of the form {{0<-> ((-a)+b)}}, correspond to control flow and
corotuining between two subcomputations -- only one of which `exists'
at any point.

>>>>

At this point we have constructed a strange mixing of two functions;
`inputs' of one form `outputs' of the other. If {{(1/alpha1,alpha2)}}
is held by one subcomputation and {{(1/alpha2,alpha1)}} is held by
another subcomputation, these `remixed functions' form a communication
channel between the subcomputations -- unifying {{1/alpha1}} with
\verb|color| {{R}} in one subcomputation, fixes it in the
other. Depending on the choice of the type {{a}}, an arbitrary number
of bits may be communicated. The dual reading of the above, with
additive functions of the form {{0<-> (-a)+b}}, correspond to
control flow and corotuining between two subcomputations -- only one
of which `exists' at any point.
